\documentclass[10pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage[margin=0.5in]{geometry}
\pagestyle{empty}

\begin{document}
\vspace*{-40pt}
\begin{center}{\Huge \scshape {Nicolas Lindbloom-Airey}}\\
SF Bay Area, CA $\cdot$ nicolas.lindbloom.airey@gmail.com $\cdot$
nclindbl@ucsc.edu $\cdot$ (650) 223-1592\\
\href{https://www.linkedin.com/in/nicolas-lindbloom-airey/}{LinkedIn} $\cdot$
linkedin.com/in/nicolas-lindbloom-airey
\end{center}

\section*{Education} \vspace*{-18pt} \hrulefill \\
\textbf{University of California, Santa Cruz}   \hfill  Santa Cruz, CA\\
\textit{Bachelors of Science in Mathematics with Magna Cum Laude}           \hfill  Sep 2018 - June 2021\\

\noindent
\textbf{University of California, Santa Cruz}   \hfill  Santa Cruz, CA\\
\textit{Masters of Arts in Mathematics}            \hfill  Sep 2021 - June 2022\\

\vspace*{-8pt} 
\noindent
\textbf{Computer Science and Physics Courses}
\begin{itemize} \itemsep -1mm
\vspace*{-6pt} 
    \item CSE 12 Data Structures, CSE 101 Algorithms, CSE 102 Analysis of Algorithms, 
    CSE 144 Machine Learning
    \item Top scoring(A+) in Analysis of Algorithms and gave a presentation about the FFT
    \item Quantum Computing, Mechanics, Wave Motion,
    Electricity \& Magnetism
    \item Wrote a python script to emulate a quantum circuit and verify its correctness.
\end{itemize}

\vspace*{-10pt}

\section*{Research Experience} \vspace*{-12pt} \hrulefill \vspace*{6pt} \\
\textbf{Math Education Research Group} \hfill University of California, Santa
Cruz, CA\\
\textit{Undergraduate research} \hfill Sep 2019 - Present\\
\begin{itemize} \itemsep -1mm
\vspace*{-10pt} 
    \item I was personally invited to join research group as an undergrad by Dr.
    Judit Moschkovich.
    \item Weekly research group where we read and discuss current and past
    research in the area of math education. We support the 3 PhD candidates with
    anything they need for their dissertations.
\end{itemize}

\section*{Work Experience} \vspace*{-12pt} \hrulefill \vspace*{6pt} \\
\textbf{Spacecraft Program Delivery at Maxar} \hfill Remote Internship\\
\textit{Software Engineer Intern} \hfill Summer 2021\\
\vspace*{-10pt} \begin{itemize} \itemsep -1mm
    \item Learning a new language?
\end{itemize}

\noindent
\textbf{Spacecraft Systems Loral at Maxar} \hfill Remote Internship\\
\textit{Software Engineer Intern} \hfill Summer 2020\\
\vspace*{-10pt} \begin{itemize} \itemsep -1mm
    \item I wrote testing scripts to do a variety of tests to ensure the
    spacecraft reacted correctly to commanding.
    \item Learned a new scripting language (Tcl) on the fly.
    \item Competed in a team-based lunar rover design challenge.
\end{itemize}

\noindent
\textbf{Jose Valdes Math Institute} \hfill Stanford University, Palo Alto, CA\\
\textit{Classroom Program Assitant} \hfill Summer 2018, Summer 2019\\
\vspace*{-10pt} \begin{itemize} \itemsep -1mm
    \item Jose Valdes is a non-profit organization that teaches math during the
    summer to local, underprivileged middle-schoolers.
    \item As a teaching assistant I helped the credentialed math teacher I was
    placed with do anything they needed, including teaching lessons.
\end{itemize}


\section*{Coding Projects} \vspace*{-12pt} \hrulefill \vspace*{6pt} \\
\textbf{Pokemon Battle Simulator} \hfill \textit{https://github.com/nicolaslindbloomairey/pokemon-python}\\
\vspace*{-10pt}

\noindent
\textbf{Taylor Swift Translator} \hfill \textit{https://github.com/nicolaslindbloomairey/taylorswifttranslator}\\
\vspace*{-10pt}

\section*{Skills} \vspace*{-12pt} \hrulefill \vspace*{6pt} \\
\begin{tabular}{ l l }
Programming Languages: & Java, C, Python, Javascript, Tcl\\
UNIX & Very comfortable with command line interface and a variety of command
line tools.\\
English and Spanish & Fluent, Reading, Writing, Speaking\\
\end{tabular}

\end{document}
